Turbulence in compact to giant HII regions

### 2022-06-29 strucfunc_paper.tex
Javier changes 2022-06-28 evening

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. Sizes taken from Table 2 of \citet{1984ApJ...287..116K}. Reference from the other properties are mentioned in the text.}
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ d& \text{Size,}\ S & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.436 \pm 0.02  & 5 \pm 0.5    &    37.18       &   9.9 \pm 1.2\FNa        \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   11.7 \pm 1.6    \\
Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    38.54    &   18.6 \pm 3.3\FNa      \\
30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &   22 \pm 2.2    \\
NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &   10.1 \pm 1.0     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   10.5 \pm 0.02\\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &   10.3 \pm 0.03     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   16.8 \pm 0.1     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   17.8 \pm 0.30     \\
\bottomrule
\multicolumn{5}{l}{\FNa{}Value obtained from our observations.}
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

@@

%Intro for scaling relations
Correlations between the physical properties of \hii{} regions like size, luminosity, and the velocity dispersion, have been used as tools for finding scaling relationships for these objects, which have also been found in dwarf galaxies and high-redshift star formation regions.
\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the \hii{} regions as the diameter or the luminosity (\(r \sim \sigma ^{\sim 2}\) ; \(\text{L}_{\text{H}} \sim \sigma ^{\sim 4}\)).
In later years, \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
%\citet{1981MNRAS.194..809L}
In recent years, \citet{2012MNRAS.422.3339W} have found that clumps and \hii{} regions follow scaling relations over the range of z = 0-2 for the \halpha\ emission line with the size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively. 
This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
Recently, \citet{Moiseev:2015a} found that the relation in dwarf galaxies is \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{5}\).
\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity and the velocity dispersion for new data of 36 giant HII regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).

%methods for our analysis
In section \ref{sec:results} we show that each velocity field of our sample can be characterized by parameters that are particular for each \hii{} region.
We used these parameters to develop scaling relations between them and the physical properties of each region.
To accomplish this we implement a hierarchical Bayesian model for fitting a straight line using the \texttt{linmix} Python library based on \cite{2007ApJ...665.1489K}.
We use the physical properties in Table \ref{tab:regions-properties} as the independent variable \(X\) and the turbulent parameters in Table \ref{tab:Res} as the dependent variable \(Y\).
In the following analysis we left out the EON to avoid redundancy in the fitting process.
For the physical properties we consider an uncertainty of \num{10}\% of the values for the size and the mean non-thermal linewidths for 30 Doradus and NGC 346.
For the turbulent parameters we use the relative error considering the 2-\(\sigma\) intervals. 
In the case of non-gaussian distribution we choose the highest value for the uncertainty.
The main results are shown in Table \ref{tab:RestStats} in ascending order for the \(p\)-value.
In the Figures \ref{fig:sigvsl}, \ref{fig:rvsR} and \ref{fig:los-vs-pos} we show the plots for the correlations with a significance level \(p < \num{0.05}\) which corresponds to the first three rows in Table \ref{tab:RestStats}.
In the Figures the black solid line shows the input regression line with its equation and the red thin lines show some samples from the posterior distribution.

%Luminosity vs centroid velocity dispersion
The Figure \ref{fig:sigvsl} shows the log \(\sigma\pos\)-log \(\text{L}(\text{H}_{\alpha})\) plane.
The references for the \(\text{L}(\text{H}_{\alpha})\) value are given in Appendix~\ref{sec:notes-individual-hii}.
Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
Our results give us a relation of \(\log \sigma\pos = (0.27 \pm 0.10) \log \text{L}(\text{H}_{\alpha})-(9.9 \pm 4.0)\).
It is customary in the literature to present \(\text{L} (\text{H}_{\alpha})\) as the dependent variable.
In our case if taking the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.6}\). 
Using the same procedure in \textit{linmix} and changing the variables order we obtained \(\log \text{L}(\text{H}_{\alpha}) = (2.8\pm 1.0) \log \sigma\pos -(36 \pm 4)\).
Both values are close to the \(\text{L}_{\text{H}} \propto \sigma^{4}\) relations.
The fact that this relation

%Size vs correlation length
The Figure \ref{fig:rvsR} shows the relation of the correlation length \(r_0\) and the size \(S\) of the region. 
The relationship we found is \(\log r_0 = (0.95 \pm 0.33) \log S - (1.6 \pm 0.7)\).
The values of \(S\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
limits seen from visual inspection of \ha{} photographs.
These values would represent an upper limit of the size of each region.
Since these objects do not posses physical edges the size determination is not trivial.
Due to the above, we chose these set values since they are from an unique source and are foreign to our calculations and observations, which reduced the bias in the scaling law we obtain.

%Size vs centroid velocity dispersion
Other important relation commonly used in the study of the interstellar medium is the diameter (or size) versus velocity dispersion.
Table \ref{tab:RestStats} shows this result for our sample in the forth row. 
This relation presents a significance level \(p > \num{0.05}\) but there are a couple of things worth mentioning.
Historically this relation is important following the work of \citet{1981MNRAS.194..809L} where he presents it in the context of molecular cloud complexes of many clouds, individual clouds, and clumps, so that size scales are studied over \(\num{0.1} < L < \SI{100}{pc}\) obtaining \(\sigma = 1.10 L ^{0.38}\). 
This relation is interpreted in terms of turbulence, particularly the Kolmogorov model which predicts a index of \num{0.33} so that larger regions presents more turbulence, and smaller regions less turbulence.
It has been argued that this correlation method is not as powerful as using statistical functions \citep{1984ApJ...277..556S} but it is interesting that the index is consistent within different phases of the interstellar medium (see first paragraph of this section).
On the other hand, we obtain \(\log \sigma\pos = (0.25 \pm 0.17) \log S - (0.2 \pm 0.38)\) which despite the large uncertainty is comparable with previous investigations within the error.

%power-law index
As for the power-law index \(m\) we can see from table \ref{tab:RestStats} that this parameter does not correlate with any other parameter or physical property, being the least reliable for determining or concluding something about the nature of the physical processes inside the regions.
On the other hand, the lack of correlation and the presence of the power-law index may be interpreted as a universal property of the velocity fluctuations independent of the observed object, which is the main consideration in the turbulence theory.

@@

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-svsL}
\caption{The log \(\sigma\pos\) - log $L(H_{\alpha})$ plane derived form our results an data in the literature. The markers indicates galactic (triangles), Magellanic (squares) and extragalactic (circles) regions. }
\label{fig:sigvsl}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-rvsS}
\caption{The log \(r_0\) - log \(S\) plane derived form our results an data in the literature. Markers represent the same regions as Fig. \ref{fig:sigvsl}. }
\label{fig:rvsR}
\end{figure}

@@

The case of the reduction in the \(\sigma\pos\) can be interpreted by the effect of \textit{project smearing} \citep{1984ApJ...277..556S}.
If we consider the case of homogeneous turbulent velocity, the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02 - 0.1.
This procedure implies depths of the order 10 to 50 times the correlation length.
In the lower limit \citet{arthur2016turbulence} mentioned the inconsistency of this interpretation for the Orion core nebula, since evidence has shown that the emitting layer thickness is of the order of \num{0.01} - \SI{0.3}{pc}.
For the most distant regions of our sample, the previous analysis would give depths of the order of magnitude of the observational box, but considering the analysis using the power-law index (see section~\ref{sec:power-index}) only NGC 595, which power-law index is \num{1.38}, would comply to this fully three-dimensional structure.
On the other hand, \citet{arthur2016turbulence} proposed another interpretation in terms of large-scale order motions, and emissivity fluctuations.
They consider an expanding shell where the mean velocity fluctuations on the plane of the sky are because the relative brightness of the redshifted and blueshifted hemispherers.
In this case, the rms fractional variation in the emissivity on the scale diameter is found to be in the order of \(\sigma\pos / \sigma_{\text{los}}\).

@@

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-los-vs-pos}
\caption{
The \(\sigma_{\text{pos}}\)-\(\langle \sigma_{\text{los}} \rangle\) plane. The diagonal gray solid lines shows the relation \(\sigma_{\text{los}}\) = \(\sigma_{\text{pos}}\) and \(\sigma_{\text{los}}\) = 2\(\sigma_{\text{pos}}\). The dashed line corresponds to the linear fit obtained by \citet{2011MNRAS.413..705L} which correspond to a sample of small-to-intermediate size \hii{} regions in M33.  Markers represent the same regions as Fig. \ref{fig:sigvsl}. 
}
\label{fig:los-vs-pos}
\end{figure}

\subsection{Kinematic relationship between ionized gas, molecular gas, and stars}
\label{sec:kinem-rela-betw}

Naively, the relatively small observed CO velocity dispersion
(\(\sigma(\chem{CO}) \ll \sigma(\ha)\) in all regions
for both \(\sigma\los\) and \(\sigma\pos\))
might be thought to rule out the molecular gas kinematics
as a \emph{cause} of the ionized gas kinematics.
However, this is not necessarily the case, so long as \emph{some} molecular gas
exists at the higher velocities typical of the ionized gas.

This is because a relatively small column of material
(\(N(\chem{H}) \sim \SI{e20}{cm^{-2}}\))
is sufficient to trap the ionization front,
in which case the \ha{} surface brightness is limited by the
incident ionizing flux
\citetext{the Ferland mechanism,
  see section~5.1 of \citealt{Baldwin:1991a}
  and section~B.2.1 of \citealt{Ferland:2012a}
}.
On the other hand, the bulk of the CO emission will come from much larger
column densities (\(N(\chem{H}) \sim \SI{e22}{cm^{-2}}\)),
where the molecules are effectively shielded from dissociation.
% If a given region can be considered as an ensemble of clouds of
% different masses, then ... would require lower mass clouds to move
% faster though, so needs dynamical relaxation

\textbf{Check  if this is actually feasible before developing further}

Very schematically, one could represent these processes as:
\begin{equation}
  \label{eq:1}
  \sigma^2(\ha) \sim \zeta \sigma^2(\chem{CO}) + \eta
\end{equation}
where \(\zeta\) is a multiplicative factor
due primarily to the saturation at the Ferland limit,
and \(\eta \sim \csound^2\) is an additive factor due to additional turbulence
generated by the transonic ionized photoevaporation flows.

\textbf{Estimate these two factors by fitting to the observations}

\subsection{Interpretation of the turbulent parameters}\label{sec:interpretation-parameters}

\subsubsection{Correlation length \(r_0\)}

Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
It is unclear what are the precise mechanisms driving the turbulence in \hii{} regions, thought a lot of options are candidates.
The most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
There are several energy sources that could provide or contribute  to the energy required: of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy and, bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work.
We can use the kinematic analysis of the regions to investigate how previously identified energy injection mechanisms could be related to the correlation length.

\citet{2009AJ....137..367O} present a three-dimensional study of the dynamic structure of the Orion nebula.
The high-velocity stellar wind from \(\theta^1\) Ori C will confine the ionized gas, even the high ionization emission lines, to a thick shell.
In one direction, at a distance of \SI{0.1}{pc} from the ionizing massive star a stationary shell of shocked material is formed when the ram pressure of the photoevaportation flow balances the thermal pressure of the shocked wind.
In the other direction there is a free flow of the hypersonic wind.
At a smaller scale of \SI{0.02}{pc} there is an interaction between the closest proplyd photoevaporation flow and the stellar wind which results in bowshocks.
According to \citet{2001ApJ...561..830G} the influence of stellar wind interactions is restricted to the central \SI{0.05}{pc}. 
Orion also present a champagne flow where the photoionized gas streams away from the ionization front covering a distance of \SI{\sim 1}{pc} from the molecular cloud \citep{1973ApJ...183..863Z}.

Our correlation length results for the Orion Core and EON from table~\ref{tab:Res}, \num{0.068} y \SI{0.39}{pc} respectively, despite been of the order of the scales mentioned above still aren't conclusive enough to determine a direct relation between them.
As mentioned in \citet{arthur2016turbulence} the mechanism mentioned in the previous paragraph would play a secondary role in stirring up the gas motions and it would be necessary to specify if the velocity fluctuations arise from pure turbulent motion inside the ionized clouds or a consequences of density and brightness fluctuations.

\citet{sabalisck1995supersonic} studied NGC 604 revealing that the high emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{\text{los}}\) $<$ \SI{20}{km.s^{-1}}.
This knots have a characteristic radius of \(\sim\)\SI{7}{pc} and a Gaussian profile.
Values of velocity dispersion $>$\SI{20}{km.s^{-1}} are found in low emission cavities where the lines present strong asymmetries.
These cavities were identified as expanding shells by \cite{yang1996} with diameters of \(\sim\)\SI{40}{pc} and a expansion velocity above \SI{50}{km.s^{-1}}.
According to table~\ref{tab:Res} the correlation length for NGC 604 is close to the scale of the bright knots in the region which aren't related to a particular energy injection mechanism.

Although the Orion core, the EON, and NGC 604 have different \(r_0\) is not clear if it truly reveal a concrete aspect of the energy input mechanism mentioned above.
Orion main energy input comes from one star, meanwhile NGC 604 has more than 200 OB stars including WR stars. 
The Orion core also presents Herbig-Haro objects, which aren't possible to resolve for more distant regions.
Though the correlation length is particular to each region, and it is correlated mainly with the size (see section~\ref{sec:scaling-relations}), it still needs further studies to reveal the true implication of this value with respect the energy input mechanisms.

\subsubsection{Structure function power-law index \(m\)}\label{sec:power-index}

The index \(m\) shown in the last column of Table \ref{tab:Res} is used for comparison between observations and the theoretical value of 0.67.
All our indices are above this theoretical value and this is attributed to the fact that the \hii{} regions do not comply with the assumptions established in the development of the turbulent theory.

>>>>

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. Diameters taken from Table 2 of \citet{1984ApJ...287..116K}. Mean non-thermal linewidth values, \(\langle \sigma\los \rangle\), shown here are corrected considering equation \eqref{eq:sigma-los} which takes into account \(\sigma_{\mathrm{fs}}\). Non-corrected \(\langle \sigma\los \rangle\) values and other properties references are mentioned in the text. }
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance} & \text{Diameter,}\ D & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.436 \pm 0.02  & 5 \pm 0.5    &    37.18       &    9.9 \pm 1.2\FNa        \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   11.2 \pm 1.6    \\
Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    38.54    &   18.6 \pm 3.3\FNa      \\
30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &     21.7 \pm 2.2    \\
NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &    9.6 \pm 1.0     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   10.0 \pm 0.02\\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &    9.8 \pm 0.03     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   16.5 \pm 0.1     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   17.5 \pm 0.30     \\
\bottomrule
\multicolumn{5}{l}{\FNa{}Value obtained from our observations.}
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

@@

%Intro for scaling relations
\textit{Maybe this paragraph it not necessary. Just a small intro and if needed previous results can be in a table for comparison. }
Correlations between the physical properties of \hii{} regions like size, luminosity, and the velocity dispersion, have been used as tools for finding scaling relationships for these objects, which have also been found in dwarf galaxies and high-redshift star formation regions.
\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the \hii{} regions as the diameter or the luminosity (\(r \sim \sigma ^{\sim 2}\) ; \(\text{L}_{\text{H}} \sim \sigma ^{\sim 4}\)).
In later years, \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
%\citet{1981MNRAS.194..809L}
In recent years, \citet{2012MNRAS.422.3339W} have found that clumps and \hii{} regions follow scaling relations over the range of z = 0-2 for the \halpha\ emission line with the size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively. 
This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
Recently, \citet{Moiseev:2015a} found that the relation in dwarf galaxies is \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{5}\).
\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity and the velocity dispersion for new data of 36 giant HII regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).

%methods for our analysis
In section \ref{sec:results} we show that each velocity field of our sample can be characterized by parameters that are particular for each \hii{} region.
We used these parameters to develop scaling relations between them and the physical properties of each region.
To accomplish this we implement a hierarchical Bayesian model for fitting a straight line using the \texttt{linmix} Python library based on \cite{2007ApJ...665.1489K}.
We use the physical properties in Table \ref{tab:regions-properties} as the independent variable \(X\) and the turbulent parameters in Table \ref{tab:Res} as the dependent variable \(Y\).
In the following analysis we left out the EON to avoid redundancy in the fitting process.
For the physical properties we consider an uncertainty of \num{10}\% of the values for the size and the mean non-thermal linewidths for 30 Doradus and NGC 346.
For the turbulent parameters we use the relative error considering the 2-\(\sigma\) intervals. 
In the case of non-gaussian distribution we choose the highest value for the uncertainty.
The main results are shown in Table \ref{tab:RestStats} in ascending order for the \(p\)-value.
In the Figures \ref{fig:sigvsl}, \ref{fig:rvsR} and \ref{fig:los-vs-pos} we show the plots for the correlations with a significance level \(p < \num{0.05}\) which corresponds to the first three rows in Table \ref{tab:RestStats}.
In the Figures the black solid line is the input regression line which is described by the equation in the plot, and the red thin lines are a random sample (\num{ \sim 400}) from the posterior distribution within one standard deviation from the slope and the \(Y\)-intercept value.

@@

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-svsL}
\caption{The log \(\sigma\pos\) - log $L(H_{\alpha})$ plane derived form our results an data in the literature. The markers indicates galactic (triangles), Magellanic (squares) and extragalactic (circles) regions. The black solid line is the input regression line which is described by the equation in the plot, and the red thin lines are a random sample (\num{ \sim 400}) from the posterior distribution within one standard deviation from the slope and the \(Y\)-intercept value. }
\label{fig:sigvsl}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-rvsS}
\caption{
Same information as Fig. \ref{fig:sigvsl} but for the log \(r_0\) - log \(S\) plane derived form our results an data in the literature. 
}
\label{fig:rvsR}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-los-vs-pos}
\caption{
Same information as Fig. \ref{fig:sigvsl} but for the \(\sigma_{\text{pos}}\)-\(\langle \sigma_{\text{los}} \rangle\) plane. The dashed line corresponds to the linear fit obtained by \citet{2011MNRAS.413..705L} which correspond to a sample of small-to-intermediate size \hii{} regions in M33. 
}
\label{fig:los-vs-pos}
\end{figure}

\subsubsection{Luminosity vs centroid velocity dispersion}\label{sec:L-vs-sigmapos}

The Figure \ref{fig:sigvsl} shows the log \(\sigma\pos\)-log \(\text{L}(\text{H}_{\alpha})\) plane.
Since this relation is common in the literature it can be use to investigate how reliable are our results and can be used as comparison with the previous investigations.
The fit we obtained give us a relation of \(\log \sigma\pos = (0.27 \pm 0.10) \log \text{L}(\text{H}_{\alpha})-(9.9 \pm 4.0)\).
Since it is customary in the literature to present \(\text{L} (\text{H}_{\alpha})\) as the dependent variable we also calculate this relation.
Taking the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.6 \pm 1.4}\). 
Using the same procedure in \textit{linmix} and changing the variables we obtain \(\log \text{L}(\text{H}_{\alpha}) = (2.8\pm 1.0) \log \sigma\pos -(36 \pm 4)\).
Both results are close to the \(\text{L}_{\text{H}} \propto \sigma^{4}\) theoretical relation.

The fact that this relationship holds in our results is interesting considering that the \(\sigma\pos\) is obtained using the structure function and the \(\text{L}(\text{H}_{\alpha})\) values comes from different sources unrelated to oour data (see the Appendix~\ref{sec:notes-individual-hii}).
This means that the proposed model describes within certain accuracy the velocity field fluctuations and that the parameters obtained can be interpreted a true property of each \hii{} region velocity field .

\subsubsection{Diameter vs correlation length}\label{sec:D-vs-r0}

The Figure \ref{fig:rvsR} shows the relation of the correlation length \(r_0\) and the diameter \(D\) of the region. 
The relationship we found is \(\log r_0 = (0.95 \pm 0.33) \log S - (1.6 \pm 0.7)\).
The values of \(D\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
limits seen from visual inspection of \ha{} photographs.
These values would represent an upper limit of the size of each region.
Since these objects do not posses physical edges the size determination is not trivial.
Due to the above, we chose these set values since they are from an unique source and are foreign to our calculations and observations, which reduced the bias in the scaling law we obtain.

Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
It is unclear what are the precise mechanisms driving the turbulence in \hii{} regions, thought a lot of options are candidates.
The most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
There are several energy sources that could provide or contribute  to the energy required: of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy and, bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work.

The dependence on \(r_0\) and the diameter can be interpreted in terms that each region presents a characteristic energy injection mechanism (or combination) and despite the presence of the different mechanisms in the regions there some unique combination that drives the input energy in each region.

@@

The case of the reduction in the \(\sigma\pos\) can be interpreted by the effect of \textit{project smearing} \citep{1984ApJ...277..556S}.
If we consider the case of homogeneous turbulent velocity, the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02 - 0.1.
This procedure implies depths of the order 10 to 50 times the correlation length.
In the lower limit \citet{arthur2016turbulence} mentioned the inconsistency of this interpretation for the Orion core nebula, since evidence has shown that the emitting layer thickness is of the order of \num{0.01} - \SI{0.3}{pc}.
%For the most distant regions of our sample, the previous analysis would give depths of the order of magnitude of the observational box, but considering the analysis using the power-law index (see section~\ref{sec:power-index}) only NGC 595, which power-law index is \num{1.38}, would comply to this fully three-dimensional structure.
On the other hand, \citet{arthur2016turbulence} proposed another interpretation in terms of large-scale order motions, and emissivity fluctuations.
They consider an expanding shell where the mean velocity fluctuations on the plane of the sky are because the relative brightness of the redshifted and blueshifted hemispherers.
In this case, the rms fractional variation in the emissivity on the scale diameter is found to be in the order of \(\sigma\pos / \sigma_{\text{los}}\).

@@

\subsubsection{Diameter vs centroid velocity dispersion}

Other important relation commonly used in the study of the interstellar medium is the diameter (or size) versus velocity dispersion.
Table \ref{tab:RestStats} shows this result for our sample in the forth row. 
This relation presents a significance level \(p > \num{0.05}\) but there are a couple of things worth mentioning.
Historically this relation is important following the work of \citet{1981MNRAS.194..809L} where he presents it in the context of molecular cloud complexes of many clouds, individual clouds, and clumps, so that size scales are studied over \(\num{0.1} < L < \SI{100}{pc}\) obtaining \(\sigma = 1.10 L ^{0.38}\).

This relation is interpreted in terms of turbulence, particularly the Kolmogorov model which predicts a index of \num{0.33} so that larger regions presents more turbulence, and smaller regions less turbulence.
It has been argued that this correlation method is not as powerful as using statistical functions \citep{1984ApJ...277..556S} but it is interesting that the index is consistent within different phases of the interstellar medium (see first paragraph of this section).
On the other hand, we obtain \(\log \sigma\pos = (0.25 \pm 0.17) \log S - (0.2 \pm 0.38)\) which despite the large uncertainty is comparable with previous investigations within the error.

As we mentioned in section \ref{sec:L-vs-sigmapos} the fact that this relation holds up to previous investigation gives some certainty that the \(\sigma\pos\) value obtained via the proposed model of the structure function is valid. 
This implying that the structure function, while not an absolute diagnostic, is a powerful tool in the research of \hii{} regions kinematics.

\subsection{Power-law index}

The power-law index \(m\) shown in the last column of Table \ref{tab:Res} is used for comparison between the observations and the theoretical value of 0.67.
All our indices are above this theoretical value and this is attributed to the fact that the \hii{} regions do not comply with the assumptions established in the development of the turbulent theory.

\hii{} regions emerged from a molecular cloud with highly filamentary and clumpy density structure .
There is a large increase in the temperature because of the photoionization, and the density gradients with the pressure gradients accelerate the flow which occurs on multiple scales consequence of the fractal nature of the molecular cloud \citep{arthur2016turbulence}.
The radiation pressure, stellar winds and region expansion, among other physical processes would create pressure-driven shock waves propagating faster than the speed of sound in the medium.
This would make the flow compressible and supersonic in \hii{} regions.
Also, as \hii{} regions are three-dimensional objects our structure function results comes from a projection of this three-dimensional structure to a two-dimensional velocity field.
But despite the complex nature of \hii{} regions and observational limitations we obtain a common pattern for the structure function and the value of the power-law index falls in a certain limited range of values. 
The differences in the power-law index with respect the theoretical value are often used as a diagnostic tools to identify properties that are not consider in the assumptions of the turbulence theory.

As for any relation of the power-law index \(m\) we can see from table \ref{tab:RestStats} that this parameter does not correlate with any other parameter or physical property, being the least reliable for determining or concluding something about the nature of the physical processes inside the regions.
On the other hand, the lack of correlation and the presence of this power-law index describing the assumed energy cascade may be interpreted as a universal property of the velocity fluctuations independent of the observed object, which is the main consideration in the turbulence theory.

%\subsection{Kinematic relationship between ionized gas, molecular gas, and stars}
%\label{sec:kinem-rela-betw}

%Naively, the relatively small observed CO velocity dispersion
%(\(\sigma(\chem{CO}) \ll \sigma(\ha)\) in all regions
%for both \(\sigma\los\) and \(\sigma\pos\))
%might be thought to rule out the molecular gas kinematics
%as a \emph{cause} of the ionized gas kinematics.
%However, this is not necessarily the case, so long as \emph{some} molecular gas
%exists at the higher velocities typical of the ionized gas.

%This is because a relatively small column of material
%(\(N(\chem{H}) \sim \SI{e20}{cm^{-2}}\))
%is sufficient to trap the ionization front,
%in which case the \ha{} surface brightness is limited by the
%incident ionizing flux
%\citetext{the Ferland mechanism,
%  see section~5.1 of \citealt{Baldwin:1991a}
%  and section~B.2.1 of \citealt{Ferland:2012a}
%}.
%On the other hand, the bulk of the CO emission will come from much larger
%column densities (\(N(\chem{H}) \sim \SI{e22}{cm^{-2}}\)),
%where the molecules are effectively shielded from dissociation.
% If a given region can be considered as an ensemble of clouds of
% different masses, then ... would require lower mass clouds to move
% faster though, so needs dynamical relaxation

%\textbf{Check  if this is actually feasible before developing further}

%Very schematically, one could represent these processes as:
%\begin{equation}
%  \label{eq:1}
%  \sigma^2(\ha) \sim \zeta \sigma^2(\chem{CO}) + \eta
%\end{equation}
%where \(\zeta\) is a multiplicative factor
%due primarily to the saturation at the Ferland limit,
%and \(\eta \sim \csound^2\) is an additive factor due to additional turbulence
%generated by the transonic ionized photoevaporation flows.

%\textbf{Estimate these two factors by fitting to the observations}

%\subsection{Interpretation of the turbulent parameters}\label{sec:interpretation-parameters}

%\subsubsection{Correlation length \(r_0\)}

%Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
%It is unclear what are the precise mechanisms driving the turbulence in \hii{} regions, thought a lot of options are candidates.
%The most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
%There are several energy sources that could provide or contribute  to the energy required: of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
%At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy and, bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
%Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work.
%We can use the kinematic analysis of the regions to investigate how previously identified energy injection mechanisms could be related to the correlation length.

%\citet{2009AJ....137..367O} present a three-dimensional study of the dynamic structure of the Orion nebula.
%The high-velocity stellar wind from \(\theta^1\) Ori C will confine the ionized gas, even the high ionization emission lines, to a thick shell.
%In one direction, at a distance of \SI{0.1}{pc} from the ionizing massive star a stationary shell of shocked material is formed when the ram pressure of the photoevaportation flow balances the thermal pressure of the shocked wind.
%In the other direction there is a free flow of the hypersonic wind.
%At a smaller scale of \SI{0.02}{pc} there is an interaction between the closest proplyd photoevaporation flow and the stellar wind which results in bowshocks.
%According to \citet{2001ApJ...561..830G} the influence of stellar wind interactions is restricted to the central \SI{0.05}{pc}. 
%Orion also present a champagne flow where the photoionized gas streams away from the ionization front covering a distance of \SI{\sim 1}{pc} from the molecular cloud \citep{1973ApJ...183..863Z}.

%Our correlation length results for the Orion Core and EON from table~\ref{tab:Res}, \num{0.068} y \SI{0.39}{pc} respectively, despite been of the order of the scales mentioned above still aren't conclusive enough to determine a direct relation between them.
%As mentioned in \citet{arthur2016turbulence} the mechanism mentioned in the previous paragraph would play a secondary role in stirring up the gas motions and it would be necessary to specify if the velocity fluctuations arise from pure turbulent motion inside the ionized clouds or a consequences of density and brightness fluctuations.

%\citet{sabalisck1995supersonic} studied NGC 604 revealing that the high emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{\text{los}}\) $<$ \SI{20}{km.s^{-1}}.
%This knots have a characteristic radius of \(\sim\)\SI{7}{pc} and a Gaussian profile.
%Values of velocity dispersion $>$\SI{20}{km.s^{-1}} are found in low emission cavities where the lines present strong asymmetries.
%These cavities were identified as expanding shells by \cite{yang1996} with diameters of \(\sim\)\SI{40}{pc} and a expansion velocity above \SI{50}{km.s^{-1}}.
%According to table~\ref{tab:Res} the correlation length for NGC 604 is close to the scale of the bright knots in the region which aren't related to a particular energy injection mechanism.
